\LARGE \bf Mean Estimation from One-Bit Measurements

### 2022-05-04 proof-no-distributed.tex
arranged appendix in two-columns

Let $\Xi$ be the set of points $\theta \in \Theta$ for which $\kappa(\theta)
= \eta(0)$.
%
Since $B_1,B_2,\ldots$ satisfy the conditions in
Theorem~\ref{theorem:non-adaptive-minimax}, $\theta$ is in $\Xi$ if and only
if $\lim_{n\to \infty} L_n(A_1,\ldots,A_n;\theta) = \eta(0)$. By
assumption, we have $B_i = \indic{X_i \in A_i}$, $A_i =
\cup_{k=1}^K (t^-_{i,k},t^+_{i,k})$, where $t^-_{i,1} \leq t^+_{i,1} \leq \ldots
\leq t^-_{i,K} \leq t^+_{i,K}$, and $t^-_{i,1}$ and $t^+_{i,K}$ may take the values
$-\infty$ and $\infty$, respectively. Denote the set of endpoints
\begin{equation*}
  E_i = \bigcup_{k=1}^{K}\{t^-_{i,k},t^+_{i,k}\},
\end{equation*}
and for $\theta$ and $\epsilon>0$, define
\begin{equation*}
  S_n(\theta, \epsilon) \triangleq \left\{ i\leq n ~ \mbox{s.t.}~
  (\theta-\epsilon,\theta+\epsilon) \cap E_i \neq \emptyset \right\}
\end{equation*}
In words, $S_n$ contains all integers smaller than $n$ in which an
$\epsilon$-ball around $\theta$ contains an endpoint of one of the intervals
defining $A_i$.
%
We now claim that 
if $\theta \in \Xi$ then $\card(S_n(\theta, \epsilon))/n \to 1$. Indeed, for such $\theta$ we have
\begin{align}
& L_n(A_1,\ldots,A_n; \theta) \nonumber \\
& = \frac{1}{n} \sum_{i \in S_n(\epsilon,\theta)}  
\frac{ \left(\sum_{k=1}^{K}  f(\theta - t^+_{i,k})- f(\theta - t^-_{i,k}) \right)^2}{ \sum_{k=1}^{K} \left( F(\theta - t^+_{i,k})- F(\theta - t^-_{i,k}) \right) \left(1-\sum_{k=1}^{K} \left( F(\theta - t^+_{i,k})- F(\theta - t^-_{i,k}) \right)\right)} \nonumber \\
& 
+ \frac{1}{n}\sum_{i \notin S_n(\epsilon,\theta) } \frac{ \left(\sum_{k=1}^{K}  f(t^+_{i,k}-\theta) - f(t^-_{i,k}-\theta) \right)^2} { \sum_{k=1}^{K} \left( F(\theta - t^+_{i,k})- F(\theta - t^-_{i,k}) \right) \left(1-\sum_{k=1}^{K} \left( F(\theta - t^+_{i,k})- F(\theta - t^-_{i,k}) \right)\right)} \nonumber \\
& \overset{(a)}{\leq}
\frac{\card\left(S_n(\theta,\epsilon)\right)}{n} \eta(0) + \frac{n-\card\left(S_n(\theta,\epsilon) \right) }{n} \eta(\epsilon) 
 \label{eq:non_existence_proof1}
\end{align}
where $(a)$ follows from Lemma~\ref{lem:bound_intervals_delta} with $\delta =0$, and the fact that for $i \in S_n(\theta, \epsilon)$, 
\begin{equation*}
\max\left\{ \max_k \eta(t^+_{i,k}-\theta) , \max_k \eta(t^-_{i,k}-\theta)  \right\} \leq \eta(\epsilon) < \eta(0). 
\end{equation*}
Unless  $\card \left(S_n(\theta, \epsilon) \right)/n \to 1$, we get that \eqref{eq:non_existence_proof1}, hence $L_n(A_1,\ldots,A_n ; \theta)$, are bounded from above by a constant that is smaller then $\eta(0)$ in contradiction to the fact that $\theta \in \Xi$.

>>>>

Let $\Xi$ be the set of points $\theta \in \Theta$ for which $\kappa(\theta)
= \eta(0)$.
%
Since $B_1,B_2,\ldots$ satisfy the conditions in
Theorem~\ref{theorem:non-adaptive-minimax}, $\theta$ is in $\Xi$ if and only
if $\lim_{n\to \infty} L_n(A_1,\ldots,A_n;\theta) = \eta(0)$. By
assumption, we have $B_i = \indic{X_i \in A_i}$, $A_i =
\cup_{k=1}^K (t^-_{i,k},t^+_{i,k})$, where $t^-_{i,1} \leq t^+_{i,1} \leq \ldots
\leq t^-_{i,K} \leq t^+_{i,K}$, and $t^-_{i,1}$ and $t^+_{i,K}$ may take the values
$-\infty$ and $\infty$, respectively. Denote the set of endpoints
\begin{equation*}
  E_i = \bigcup_{k=1}^{K}\{t^-_{i,k},t^+_{i,k}\},
\end{equation*}
and for $\theta$ and $\epsilon>0$, define
\begin{equation*}
  S_n(\theta, \epsilon) \triangleq \left\{ i\leq n ~ \mbox{s.t.}~
  (\theta-\epsilon,\theta+\epsilon) \cap E_i \neq \emptyset \right\}
\end{equation*}
In words, $S_n$ contains all integers smaller than $n$ in which an
$\epsilon$-ball around $\theta$ contains an endpoint of one of the intervals
defining $A_i$.
%
We now claim that 
if $\theta \in \Xi$ then $\card(S_n(\theta, \epsilon))/n \to 1$. 
Indeed, for such $\theta$ we have
\begin{align}
& L_n(A_1,\ldots,A_n; \theta) \nonumber \\
& = \frac{1}{n} \sum_{i \in S_n(\epsilon,\theta)}  
\frac{ \left(\sum_{k=1}^{K}  f(\theta - t^+_{i,k})- f(\theta - t^-_{i,k}) \right)^2}{ \sum_{k=1}^{K} \left( F(\theta - t^+_{i,k})- F(\theta - t^-_{i,k}) \right)} \nonumber \\
& \qquad \times \frac{1} {\left(1-\sum_{k=1}^{K} \left( F(\theta - t^+_{i,k})- F(\theta - t^-_{i,k}) \right)\right)} \nonumber \\
& 
+ \frac{1}{n}\sum_{i \notin S_n(\epsilon,\theta) } \frac{ \left(\sum_{k=1}^{K}  f(t^+_{i,k}-\theta) - f(t^-_{i,k}-\theta) \right)^2} { \sum_{k=1}^{K} \left( F(\theta - t^+_{i,k})- F(\theta - t^-_{i,k}) \right)} \nonumber \\
& \qquad \times \frac{1} {\left(1-\sum_{k=1}^{K} \left( F(\theta - t^+_{i,k})- F(\theta - t^-_{i,k}) \right)\right)} \nonumber \\
& \le
\frac{\card\left(S_n(\theta,\epsilon)\right)}{n} \eta(0) + \frac{n-\card\left(S_n(\theta,\epsilon) \right) }{n} \eta(\epsilon) 
 \label{eq:non_existence_proof1}
\end{align}
where the last transition follows from Lemma~\ref{lem:bound_intervals_delta} with $\delta =0$ and the fact that for $i \in S_n(\theta, \epsilon)$, 
\begin{equation*}
\max\left\{ \max_k \eta(t^+_{i,k}-\theta) , \max_k \eta(t^-_{i,k}-\theta)  \right\} \leq \eta(\epsilon) < \eta(0). 
\end{equation*}
Unless  $\card \left(S_n(\theta, \epsilon) \right)/n \to 1$, we get that \eqref{eq:non_existence_proof1}, hence $L_n(A_1,\ldots,A_n ; \theta)$, are bounded from above by a constant that is smaller then $\eta(0)$ in contradiction to the fact that $\theta \in \Xi$.
